Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1 and ERC project 280053 (CPROVER).}

### 2017-02-03 hscc2017/paper.tex

\item Experimental results show that \tool is able to efficiently synthesize
  stable controllers for a set of intricate benchmarks taken from the
  literature: the median runtime for our benchmark set with the two-stage 
  verification engine is $52$\,s, i.e.,
  half of the controllers can be synthesized in less than five minutes.

@@

Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (i.e.,
$\Delta_p{G}_n(s),\Delta_p{G}_d(s)$, which arise from tolerances/imprecision
in the original model), errors in the numeric calculations, or roundoffs in
the quantization.  These uncertainties are parametrically expressed by
additive terms, resulting in an uncertain model $\hat{G}(z)$, such that:
%
\begin{equation}
\hat{G}(z)=\frac{G_n(z)+\Delta G_n(z)}{G_d(z)+\Delta G_d(z)},
\end{equation}
%
\red{[what is the relationship between the deltas in this formula, and those in the previous paragraph? please clarify and hopefully simplify formulae. ]}
which will be represented by the following transfer function:
%
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}} : N_G \geq M_G .
\end{equation}
%
\red{[why is this condition on the order of the polynomials raised only now? how is it used later?]}
Due to the nature of the methods we use for the stability check, we require
that the parametric errors in the plant have the same polynomial order as
the plant itself (\blue{all other errors described in this paper are ensured to
fulfil this property in our implementation}\red{[have we later argued that this is indeed the case?]}) 
\blue{and that enter the plant linearly}.

>>>>

\item Experimental results show that \tool is able to efficiently synthesize
  stable controllers for a set of intricate benchmarks taken from the
  literature: the median runtime for our benchmark set considering the faster 
	engine is $48$\,s, i.e., half of the controllers can be synthesized in less than one minute.

@@

Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (i.e.,
$\Delta_p{G}_n(s),\Delta_p{G}_d(s)$, which arise from tolerances/imprecision
in the original model), errors in the numeric calculations, or roundoffs in
the quantization.  These uncertainties are parametrically expressed by
additive terms, resulting in an uncertain model $\hat{G}(z)$, such that:
%
\begin{equation}
\hat{G}(z)=\frac{G_n(z)+\Delta G_n(z)}{G_d(z)+\Delta G_d(z)},
\end{equation}
%
%\red{[what is the relationship between the deltas in this formula, and those in the previous paragraph? please clarify and hopefully simplify formulae. ]}
which will be represented by the following transfer function:
%
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}} : N_G \geq M_G .
\end{equation}
%
%\red{[why is this condition on the order of the polynomials raised only now? how is it used later?]}
Due to the nature of the methods we use for the stability check, we require
that the parametric errors in the plant have the same polynomial order as
the plant itself (\blue{all other errors described in this paper are ensured to
fulfil this property in our implementation}
%\red{[have we later argued that this is indeed the case?]}) 
%\blue{and that enter the plant linearly}.
